---
title: "6.2_spatial_model_selection_2020model"
author: "Junhong Duan"
date: "2024-09-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r cars}
library(sf) #to import shapefiles
library(spdep) #for spatial weights, spatial autocorrelation
library(spatialreg) #for spatial regression
library(lmtest) #for LM test
library(sp)
library(ggplot2)
library(viridisLite)
library(viridis)
library(dplyr)
library(beepr)
library(tidyverse)
library(sf)
library(spdep)
library(RColorBrewer)
library(spatialreg)
```

## create spatial matrix
```{r}
cbshape_sf <- st_read("../Data/311_Oakland/data_2020_ready_for_spatialModel.shp")#--------------------------改---------------------------
cbshape_sf_no_na <- cbshape_sf[!is.na(cbshape_sf$MH_prevale), ]
row.names(cbshape_sf_no_na) <- cbshape_sf_no_na$GEOID10
coords <- st_coordinates(st_centroid(cbshape_sf_no_na))
dist_matrix <- as.matrix(dist(coords))
threshold = 1000
adj_matrix_1000 <- matrix(0, nrow = nrow(dist_matrix), ncol = ncol(dist_matrix))
for (i in 1:nrow(dist_matrix)) {
  for (j in 1:ncol(dist_matrix)) {
    if (dist_matrix[i, j] <= 1000) {
      adj_matrix_1000[i, j] <- 1  # 临界距离内的权重设置为1
    } else {
      adj_matrix_1000[i, j] <- 1 / (dist_matrix[i, j] + 1e-10)  # 临界距离之外的权重按反距离设置
    }
  }
}
diag(adj_matrix_1000) <- 0
listw_1000 <- mat2listw(adj_matrix_1000, style = "W")

# threshold = 2200
adj_matrix_2200 <- matrix(0, nrow = nrow(dist_matrix), ncol = ncol(dist_matrix))
for (i in 1:nrow(dist_matrix)) {
  for (j in 1:ncol(dist_matrix)) {
    if (dist_matrix[i, j] <= 2200) {
      adj_matrix_2200[i, j] <- 1  # 临界距离内的权重设置为1
    } else {
      adj_matrix_2200[i, j] <- 1 / (dist_matrix[i, j] + 1e-10)  # 临界距离之外的权重按反距离设置
    }
  }
}
diag(adj_matrix_2200) <- 0
listw_2200 <- mat2listw(adj_matrix_2200, style = "W")

# threshold = 3000
adj_matrix_3000 <- matrix(0, nrow = nrow(dist_matrix), ncol = ncol(dist_matrix))
for (i in 1:nrow(dist_matrix)) {
  for (j in 1:ncol(dist_matrix)) {
    if (dist_matrix[i, j] <= 3000) {
      adj_matrix_3000[i, j] <- 1  # 临界距离内的权重设置为1
    } else {
      adj_matrix_3000[i, j] <- 1 / (dist_matrix[i, j] + 1e-10)  # 临界距离之外的权重按反距离设置
    }
  }
}
diag(adj_matrix_3000) <- 0
listw_3000 <- mat2listw(adj_matrix_3000, style = "W")

## 保存邻接矩阵
saveRDS(listw_1000, file = "../spatial matrix/2020/CB_listw_1000.rds") 
saveRDS(listw_2200, file = "../spatial matrix/2020/CB_listw_2200.rds") 
saveRDS(listw_3000, file = "../spatial matrix/2020/CB_listw_3000.rds") 
```


## spatial dependence dignosis
```{r}
cbshape_sf <- st_read("../Data/311_Oakland/data_2020_ready_for_spatialModel.shp")#--------------------------改---------------------------
cbshape_sf_no_na <- cbshape_sf[!is.na(cbshape_sf$MH_prevale), ]
formulas <- list(
  MH_prevale ~ STREETSW,
  MH_prevale ~ METER_REPA,
  MH_prevale ~ TREES,
  MH_prevale ~ ILLDUMP,
  MH_prevale ~ DRAINAGE,
  MH_prevale ~ SEWERS,
  MH_prevale ~ FIRE,
  MH_prevale ~ ELECTRICAL,
  MH_prevale ~ DRAINAGE + ELECTRICAL + ILLDUMP + METER_REPA + SEWERS + STREETSW + TREES,
  MH_prevale ~ DRAINAGE + ILLDUMP + METER_REPA + SEWERS + STREETSW + TREES,
  MH_prevale ~ DRAINAGE + ELECTRICAL + ILLDUMP + METER_REPA + STREETSW + TREES,
  MH_prevale ~ DRAINAGE + ILLDUMP + METER_REPA + STREETSW + TREES,
  MH_prevale ~ DRAINAGE + ELECTRICAL + ILLDUMP + METER_REPA + SEWERS + TREES,
  MH_prevale ~ DRAINAGE + ELECTRICAL + ILLDUMP + SEWERS + TREES
)
listw_1000 <- readRDS(file = "../spatial matrix/2020/CB_listw_1000.rds")
listw_1600 <- readRDS(file = "../spatial matrix/2020/CB_listw_1600.rds")
listw_2200 <- readRDS(file = "../spatial matrix/2020/CB_listw_2200.rds")
listw_3000 <- readRDS(file = "../spatial matrix/2020/CB_listw_3000.rds")

listws <- list(
  listw_1000,
  listw_1000,
  listw_1600,
  listw_1600,
  listw_2200,
  listw_2200,
  listw_2200,
  listw_3000,
  listw_1600,
  listw_1600,
  listw_1600,
  listw_1600,
  listw_1600,
  listw_1600
)
names <- list(
  'STR',
  'MET',
  'TRE',
  'ILL',
  'DRA',
  'SEW',
  'FIR',
  'ELE',
  'A',
  'B',
  'C',
  'D',
  'E',
  'F'
)

library(spatialreg)
library(lmtest)

output_file <- paste0("../spatial diagnosis/output_2020model.txt")
sink(output_file)
  
# model <- lm(MH_prevale ~ X, data = cbshape_sf_no_na)
for (i in 1:(length(formulas))) {
  
  
  print("*************************************")
  print(names[[i]])
  
  X <- as.formula(formulas[[i]])
  listw <- listws[[i]]
  model <- lm(X, data = cbshape_sf_no_na)
  lm_tests <- lm.RStests (model, listw = listw, test = c("LMlag", "LMerr", "RLMlag", "RLMerr"))
  summary(lm_tests)
  
  lm_lag_test <- lm_tests$RSlag
  lm_err_test <- lm_tests$RSerr
  robust_lm_lag_test <- lm_tests$adjRSlag 
  robust_lm_err_test <- lm_tests$adjRSerr 
  
  # Print p-values
  print(paste("P-value for LMlag test:", lm_lag_test$p.value))
  print(paste("P-value for LMerr test:", lm_err_test$p.value))
  print(paste("P-value for Robust LMlag test:", robust_lm_lag_test$p.value))
  print(paste("P-value for Robust LMerr test:", robust_lm_err_test$p.value))
 
}


sink()
```

## run models
```{r}
cbshape_sf <- st_read("../Data/311_Oakland/data_2020_ready_for_spatialModel.shp")#--------------------------改---------------------------
cbshape_sf_no_na <- cbshape_sf[!is.na(cbshape_sf$MH_prevale), ]

output_file <- paste0("../spatial model selection/output_2020model.txt")
sink(output_file)

formulas <- list(
  MH_prevale ~ STREETSW,
  MH_prevale ~ METER_REPA,
  MH_prevale ~ TREES,
  MH_prevale ~ ILLDUMP,
  MH_prevale ~ DRAINAGE,
  MH_prevale ~ SEWERS,
  MH_prevale ~ FIRE,
  MH_prevale ~ ELECTRICAL,
  MH_prevale ~ DRAINAGE + ELECTRICAL + ILLDUMP + METER_REPA + SEWERS + STREETSW + TREES,
  MH_prevale ~ DRAINAGE + ILLDUMP + METER_REPA + SEWERS + STREETSW + TREES,
  MH_prevale ~ DRAINAGE + ELECTRICAL + ILLDUMP + METER_REPA + STREETSW + TREES,
  MH_prevale ~ DRAINAGE + ILLDUMP + METER_REPA + STREETSW + TREES,
  MH_prevale ~ DRAINAGE + ELECTRICAL + ILLDUMP + METER_REPA + SEWERS + TREES,
  MH_prevale ~ DRAINAGE + ELECTRICAL + ILLDUMP + SEWERS + TREES
)
listw_1000 <- readRDS(file = "../spatial matrix/2020/CB_listw_1000.rds")
listw_1600 <- readRDS(file = "../spatial matrix/2020/CB_listw_1600.rds")
listw_2200 <- readRDS(file = "../spatial matrix/2020/CB_listw_2200.rds")
listw_3000 <- readRDS(file = "../spatial matrix/2020/CB_listw_3000.rds")


listws <- list(
  listw_1000,
  listw_1000,
  listw_1600,
  listw_1600,
  listw_2200,
  listw_2200,
  listw_2200,
  listw_3000,
  listw_1600,
  listw_1600,
  listw_1600,
  listw_1600,
  listw_1600,
  listw_1600
)

names <- list(
  'STR',
  'MET',
  'TRE',
  'ILL',
  'DRA',
  'SEW',
  'FIR',
  'ELE',
  'A',
  'B',
  'C',
  'D',
  'E',
  'F'
)
row.names(cbshape_sf_no_na) <- cbshape_sf_no_na$GEOID10
for (i in 1:(length(formulas))){
  print("*****************************************")
  print(names[[i]])
  X <- as.formula(formulas[[i]])
  listw <- listws[[i]]

  lag_model <- lagsarlm(X, data = cbshape_sf_no_na, listw = listw, zero.policy = TRUE)
  print(summary(lag_model))
  print("finish SLM model fitting")
  error_model <- errorsarlm(X, data = cbshape_sf_no_na, listw = listw, zero.policy = TRUE)
  print(summary(error_model))
  print(moran.mc(residuals(error_model), listws[[i]], zero.policy = TRUE, nsim=999))
  print("finish SEM model fitting")
  attr(listw, "region.id") <- cbshape_sf_no_na$GEOID10
  sdm_model <- lagsarlm(X, data = cbshape_sf_no_na, listw = listw, type = "Durbin", zero.policy = TRUE)
  print(summary(sdm_model))
  print("finish SDM model fitting")
  beep(sound = 3)

  saveRDS(lag_model, file = paste0("../spatial model selection/2020/slm_model_", names[i], ".rds"))
  saveRDS(error_model, file = paste0("../spatial model selection/2020/sem_model_", names[i], ".rds"))
  saveRDS(sdm_model, file = paste0("../spatial model selection/2020/sdm_model_", names[i], ".rds"))
  
}

sink()
```


## hotspot analysis
```{r}
listw_1000_next <- readRDS(file = "../spatial matrix/2021/CB_listw_1000.rds")
listw_1600_next <- readRDS(file = "../spatial matrix/2021/CB_listw_1600.rds")
listw_2200_next <- readRDS(file = "../spatial matrix/2021/CB_listw_2200.rds")
listw_3000_next <- readRDS(file = "../spatial matrix/2021/CB_listw_3000.rds")

formulas <- list(
  MH_prevale ~ STREETSW,
  MH_prevale ~ METER_REPA,
  MH_prevale ~ TREES,
  MH_prevale ~ ILLDUMP,
  MH_prevale ~ DRAINAGE,
  MH_prevale ~ SEWERS,
  MH_prevale ~ FIRE,
  MH_prevale ~ ELECTRICAL,
  MH_prevale ~ DRAINAGE + ELECTRICAL + ILLDUMP + METER_REPA + SEWERS + STREETSW + TREES,
  MH_prevale ~ DRAINAGE + ILLDUMP + METER_REPA + SEWERS + STREETSW + TREES,
  MH_prevale ~ DRAINAGE + ELECTRICAL + ILLDUMP + METER_REPA + STREETSW + TREES,
  MH_prevale ~ DRAINAGE + ILLDUMP + METER_REPA + STREETSW + TREES,
  MH_prevale ~ DRAINAGE + ELECTRICAL + ILLDUMP + METER_REPA + SEWERS + TREES,
  MH_prevale ~ DRAINAGE + ELECTRICAL + ILLDUMP + SEWERS + TREES
)

listws_next <- list(
  listw_1000_next,
  listw_1000_next,
  listw_1600_next,
  listw_1600_next,
  listw_2200_next,
  listw_2200_next,
  listw_2200_next,
  listw_3000_next,
  listw_1600_next,
  listw_1600_next,
  listw_1600_next,
  listw_1600_next,
  listw_1600_next,
  listw_1600_next
)

names <- list(
  'STR',
  'MET',
  'TRE',
  'ILL',
  'DRA',
  'SEW',
  'FIR',
  'ELE',
  'A',
  'B',
  'C',
  'D',
  'E',
  'F'
)
for (i in 1:(length(formulas))) {
  X <- as.formula(formulas[[i]])
  listw_next <- listws_next[[i]]
  lag_model <- readRDS(paste0("../spatial model selection/2020/slm_model_", names[i], ".rds"))
  error_model <- readRDS(paste0("../spatial model selection/2020/sem_model_", names[i], ".rds"))
  sdm_model <- readRDS(paste0("../spatial model selection/2020/sdm_model_", names[i], ".rds"))
  
  cbshape_sf_next <- st_read("../Data/311_Oakland/data_2021_ready_for_spatialModel.shp")#--------------------------改-----------------------
  cbshape_sf_no_na_next <- cbshape_sf_next[!is.na(cbshape_sf_next$MH_prevale), ]
  row.names(cbshape_sf_no_na_next) <- cbshape_sf_no_na_next$GEOID10
  
  attr(listw_next, "region.id") <- cbshape_sf_no_na_next$GEOID10
  
  predicted_values_lag <- predict(lag_model, newdata = cbshape_sf_no_na_next, listw = listw_next, zero.policy = TRUE, legacy.mixed=TRUE)
  save(predicted_values_lag, file = paste0("../hotspot prediction/model2020_pred2021/predicted_", names[i], "_SLM.RData"))
  print("finish SLM model predicting")

  predicted_values_err <- predict(error_model, newdata = cbshape_sf_no_na_next, listw = listw_next, zero.policy = TRUE, legacy.mixed=TRUE)
  save(predicted_values_err, file = paste0("../hotspot prediction/model2020_pred2021/predicted_", names[i], "_SEM.RData"))
  print("finish SEM model predicting")
  
  # cbshape_sf_no_na_2021 <- cbshape_sf_no_na_2021[cbshape_sf_no_na_2021$GEOID10 %in% cbshape_sf_no_na$GEOID10, ]
  attr(listw_next, "region.id") <- row.names(cbshape_sf_no_na_next)
  
  predicted_values_durbin <- predict(sdm_model, newdata = cbshape_sf_no_na_next, listw = listw_next, zero.policy = TRUE, legacy.mixed=TRUE)
  save(predicted_values_durbin, file = paste0("../hotspot prediction/model2020_pred2021/predicted_", names[i], "_refine_SDM.RData"))
  print("finish SDM model predicting")
  beep(sound = 3)
  
  cbshape_sf_no_na_next$predicted_values_lag <- as.numeric(predicted_values_lag)
  # p <- ggplot(data = cbshape_sf_no_na_next) +
  #   geom_sf(aes(fill = predicted_values_lag)) +
  #   scale_fill_viridis_c() +
  #   theme_minimal() +
  #   labs(title = "SLM: Predicted Values of MH_prevale",
  #        fill = "Predicted Value")
  # ggsave(filename = paste0("Predicted_value_maps/SLM-Predicted_Values-",names[i],".png"), plot = p, width = 10, height = 8, dpi = 300)
  # print("finish SLM map")
  # 
  cbshape_sf_no_na_next$predicted_values_err <- as.numeric(predicted_values_err)
  # p1 <- ggplot(data = cbshape_sf_no_na_next) +
  #   geom_sf(aes(fill = predicted_values_err)) +
  #   scale_fill_viridis_c() +
  #   theme_minimal() +
  #   labs(title = "SEM: Predicted Values of MH_prevale",
  #        fill = "Predicted Value")
  # ggsave(filename = paste0("Predicted_value_maps/SEM-Predicted_Values-",names[i],".png"), plot = p1, width = 10, height = 8, dpi = 300)
  # print("finish SEM map")
  # 
  cbshape_sf_no_na_next$predicted_values_durbin <- as.numeric(predicted_values_durbin)
  # p2 <- ggplot(data = cbshape_sf_no_na_next) +
  #   geom_sf(aes(fill = predicted_values_durbin)) +
  #   scale_fill_viridis_c() +
  #   theme_minimal() +
  #   labs(title = "SDM: Predicted Values of MH_prevale",
  #        fill = "Predicted Value")
  # ggsave(filename = paste0("./maps/SDM-Predicted_Values-",names[i],"_refine.png"), plot = p2, width = 10, height = 8, dpi = 300)
  # print("finish SDM map")
  print("-------------------------------------------------")
  beep(sound = 3)
}

#提取：
# slm_loaded <- readRDS("slm_model.rds")
# summary(readRDS("../Data after OLS and spatial models/sdm_model_STREETSW.rds"))

```

```{r}
library(tidyverse)
library(sf)
library(spdep)
library(RColorBrewer)

custom_colors <- c(
    "Hotspot - 99% Confidence" = "#67001F",
    "Hotspot - 95% Confidence" = "#B2182B",
    "Hotspot - 90% Confidence" = "#D6604D",
    "Not Significant" = "#F7F7F7",
    "Coldspot - 90% Confidence" = "#92C5DE",
    "Coldspot - 95% Confidence" = "#4393C3",
    "Coldspot - 99% Confidence" = "#2166AC")

for (i in 1:((length(names)))) {
  load_path <- paste0("../hotspot prediction/model2020_pred2021/predicted_", names[i], "_refine_SDM.RData")
  load(load_path)
  predicted_values_durbin <- as.data.frame(get(ls(pattern = "predicted_values_durbin")))$fit
  pred_name <- paste0(names[i],"_pred")
  cbshape_sf_no_na_next[[pred_name]] <- predicted_values_durbin
}

calculate_gi_star <- function(data, variable, listw) {
  gi_star <- localG(data[[variable]], listw)
  gi_star_col <- paste0(variable, "_Gi_star")
  significance_col <- paste0(variable, "_classification")  # renaming for clarity
  data[[gi_star_col]] <- gi_star
  data[[significance_col]] <- case_when(
    data[[gi_star_col]] >= qnorm(0.995) ~ "Hotspot - 99% Confidence",
    data[[gi_star_col]] >= qnorm(0.975) ~ "Hotspot - 95% Confidence",
    data[[gi_star_col]] >= qnorm(0.95) ~ "Hotspot - 90% Confidence",
    data[[gi_star_col]] <= qnorm(0.005) ~ "Coldspot - 99% Confidence",
    data[[gi_star_col]] > qnorm(0.005) & data[[gi_star_col]] <= qnorm(0.025) ~ "Coldspot - 95% Confidence",
    data[[gi_star_col]] > qnorm(0.025) & data[[gi_star_col]] <= qnorm(0.05) ~ "Coldspot - 90% Confidence",
    TRUE ~ "Not Significant"
  )
  return(data)
}

# perform_hotspot_analysis <- function(data, listw) {
for (i in 1:((length(names)))){ #(column in columns) {
    pred_name <- paste0(names[i],"_pred")
    cbshape_sf_no_na_next <- calculate_gi_star(cbshape_sf_no_na_next, pred_name, listws_next[[i]])
    column_name <- paste0(pred_name, "_classification")
    # cbshape_sf_no_na$column_name <- pred_classification
    
    plot <- ggplot(cbshape_sf_no_na_next) +
      geom_sf(aes(fill = .data[[column_name]]), color = "black", lwd = 0.1) +
      scale_fill_manual(values = custom_colors) +
      theme_void() +
      labs(
        fill = "Hot Spot Classification",
        title = paste("Getis-Ord Gi* Hotspot Analysis for", pred_name)
      )
    print(plot)
    ggsave(
      filename = paste("../hotspot prediction/model2020_pred2021/img/Refine_",names[i],".png"),
      plot = plot,
      width = 10,    # 图像的宽度，单位为英寸
      height = 8,    # 图像的高度，单位为英寸
      dpi = 300      # 分辨率，单位为dpi
    )
}

cbshape_sf_no_na_next <- calculate_gi_star(cbshape_sf_no_na_next, "MH_prevale", listw_1600_next)
plot <- ggplot(cbshape_sf_no_na_next) +
  geom_sf(aes(fill = .data[["MH_prevale_classification"]]), color = "black", lwd = 0.1) +
  scale_fill_manual(values = custom_colors) +
  theme_void() +
  labs(
    fill = "Hot Spot Classification",
    title = paste("Getis-Ord Gi* Hotspot Analysis for Mental Health Prevalence")
  )
print(plot)
ggsave(
  filename = "../hotspot prediction/model2020_pred2021/img/Refine_MHprev.png",
  plot = plot,
  width = 10,    # 图像的宽度，单位为英寸
  height = 8,    # 图像的高度，单位为英寸
  dpi = 300      # 分辨率，单位为dpi
)